Mamba-Based Tumor Segmentation\\ \thanks{$\dagger$ Equal contributions}

### 2024-04-26 paper/main.tex
naming

% First appendix section
\subsection{Training}
We train multiple models for image segmentation using an 80-10-10 train-test-evaluation split. The accuracy of the models is evaluated using Dice scores, and the DiceLoss is used as the loss function.  \\
PP-UMamba, UMambaBot, ResNet18, ResNet50, and UNet were trained for 100 epochs using DiceLoss as the loss function and Adam as the optimizer with a learning rate of 3e-4.\\
UltraLight-VM-UNet and UltraLight-VM-UNet\_v1-v6 were trained for 100 epochs using BCEDiceLoss as the loss function and AdamW as the optimizer with a learning rate of 3e-4. All UltraLight variants (v1-v6) are trained using the same settings as UltraLight-VM-UNet. \\
SegFormer was trained for 100 epochs using BCEWithLogitsLoss as the loss function and AdamW as the optimizer with a learning rate of 1e-4. The learning rate is reduced on a plateau using a scheduler, and early stopping is employed. \\
More detailed training information can be found in our GitHub repository: \url{https://github.com/lxaw/mamba-tumor-seg/} and under the \texttt{tests} folder.

>>>>

% First appendix section
\subsection{Training}
We train multiple models for image segmentation using an 80-10-10 train-test-evaluation split. The accuracy of the models is evaluated using Dice scores, and the DiceLoss is used as the loss function.  \\
UMambaBot-PP, UMambaBot, ResNet18, ResNet50, and UNet were trained for 100 epochs using DiceLoss as the loss function and Adam as the optimizer with a learning rate of 3e-4.\\
UL-VM-UNet and UL-VM-UNet-v1 through v6 were trained for 100 epochs using BCEDiceLoss as the loss function and AdamW as the optimizer with a learning rate of 3e-4.  \\
SegFormer was trained for 100 epochs using BCEWithLogitsLoss as the loss function and AdamW as the optimizer with a learning rate of 1e-4. The learning rate is reduced on a plateau using a scheduler, and early stopping is employed. \\
More detailed training information can be found in our GitHub repository: \url{https://github.com/lxaw/mamba-tumor-seg/} and under the \texttt{tests} folder.
